---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LYFtools

<!-- badges: start -->
<!-- badges: end -->

The `LYFtools` package is a collection of some of my frequently used functions for easy use.

# Installation

If you're interested, you can install the development version of `LYFtools` like so:

```
devtools::install_github('evanliu3594/LYFtools')
```

# Examples

There are some basic examples which shows you how to use `LYFtools`:

## random functions

### `larger_bbox()` 

`larger_bbox()` is used to get a broader bounding box of a given sf/sfc object. The result is more suitable for generating a fishnet raster.

```{r}
library(LYFtools)
library(tidyverse)

sf::st_bbox(mapchina::china) %>% 
  stars::st_as_stars(dx = 0.1, dy = 0.1)

larger_bbox(mapchina::china, precise = 0.1) %>% 
  stars::st_as_stars(dx = 0.1, dy = 0.1)
```

### `simple_date()`
`simple_date()` is to acquire a abbreviation of the date.
```{r}
simple_date()
simple_date(as.Date("2023-09-09"))
simple_date("2025-12-28")

# useful when generating filenames
str_glue("./this_is_the_filename_with_creating_date_{simple_date()}.R")
```

### `convert_amount()`
`convert_amount()` is used for convert and reform the values between Chinese quantifiers

```{r}
convert_amount(66, "兆瓦", "万千瓦")

convert_amount(1.7, "米", "毫米")

convert_amount(9600000, "平方公里", "平方米")
```

### `convert_coord()`
`convert_coord()` is used for convert a set of geo-coding (long, lat) between some Chinese defined coordinate systems and WGS1984 coordinate system. Note that only works inside China domain

```{r}
convert_coord(133, 47, from = "GCJ02", to = "WGS84")
```

## AQI_related_funs

根据中华人民共和国生态环境部《环境空气质量指数（AQI）技术规定（HJ633—2012）》中的相关标准和方法，提供五个用于计算AQI的函数

### `DaliyMeanConc()`
`DaliyMeanConc()` calculates daily mean concentration of 6 pollutants. Note that average `O3` concentration for one day is presented by maximum 8-hour average concentration.

```{r}
C <- rnorm(24, 35, 5)
DaliyMeanConc("PM2.5", C)
```

### `IAQI_hourly()`
`IAQI_hourly()` is for calculate hourly IAQI for a given pollutant
```{r}
IAQI_hourly("O3", 142)
```

### `Calc_Hourly_AQI()`
`Calc_Hourly_AQI()` calculates the hourly AQI score and the featured pollutants based on 4 pollutants' concentration.

```{r}
Calc_Hourly_AQI(SO2 = 300,NO2 = 200,CO = 100,O3 = 120)
```

### `IAQI_Daily()`
`IAQI_Daily()` calculates daily IAQI for given pollutant

```{r}
IAQI_Daily("O3", 142)
```

### `Calc_Daily_AQI()`
`Calc_Daily_AQI()` calculate the daily AQI score and the featured pollutants based on 6 pollutants' concentration.

```{r}
Calc_Daily_AQI(SO2 = 55, NO2 = 23, CO = 12, O3 = 122, PM2.5 = 35, PM10 = 55)
```

### A sample workflow with AQI series functions in `tidyr` syntax.

```{r}
# generating sample data

set.seed(3594)

sampleConc <- data.frame(
  Time = 0:23,
  SO2 = rnorm(24, mean = 300, sd = 20),
  NO2 = rnorm(24, mean = 800, sd = 100),
  O3 = rnorm(24, mean = 50, sd = 15),
  CO = rnorm(24, mean = 25, sd = 10),
  PM2.5 = rnorm(24, mean = 200, sd = 50),
  PM10 = rnorm(24, mean = 350, sd = 100)
)

sampleConc
```

```{r}
## Calculate hourly IAQI and AQI
sampleConc %>% 
  pivot_longer(-Time, names_to = 'Pollu', values_to = 'Conc') %>% rowwise() %>% 
  mutate(IAQI_h = IAQI_hourly(Pollu = Pollu, Conc = Conc)) %>% select(-Conc) %>% 
  pivot_wider(names_from = 'Pollu', values_from = 'IAQI_h')

sampleConc %>% rowwise() %>% mutate(
  AQI_h = Calc_Hourly_AQI(SO2 = SO2, NO2 = NO2,CO = CO,O3 = O3), .keep = 'none'
)
```
```{r}
## Calculate Daily Concentration and daily AQI

sampleConc_daily_mean <- sampleConc %>% select(-Time) %>% 
  imap_dbl(~DaliyMeanConc(Pollu = .y, Conc = .x))

sampleConc_daily_mean

sampleConc_daily_mean %>% imap_dbl(~IAQI_Daily(Pollu = .y, Conc = .x))

Calc_Daily_AQI(SO2 = sampleConc_daily_mean[["SO2"]],
               NO2 = sampleConc_daily_mean[["NO2"]],
               CO = sampleConc_daily_mean[["CO"]],
               PM10 = sampleConc_daily_mean[["PM10"]],
               PM2.5 = sampleConc_daily_mean[["PM2.5"]],
               O3 = sampleConc_daily_mean[["O3"]])
```
