---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LYFtools

<!-- badges: start -->

<!-- badges: end -->

The `LYFtools` package is a collection of some of my frequently used functions for easy use.

# Installation

If you're interested, you can install the development version of `LYFtools` like so:

```
devtools::install_github('evanliu3594/LYFtools')
```

# Examples

There are some basic examples which shows you how to use `LYFtools`:

## Data incorporated

### `all_cn_chr`

A regex syntax to retrieve all Chinese characters form a string.

```{r}
library(LYFtools)
library(tidyverse)
stringr::str_extract("1234567，走南闯北吃东西abcdefg", all_cn_chr)
```
### `cncrs`

A Albert projection setting to get better view of China map, see examples in later mapping components.

### `cnmap_counties`

County-level map of China, a sf object. Inherited and simplied from `mapchina` package.

```{r}
cnmap_counties %>% ggplot() + geom_sf()
```

```{r}
# see difference when projecting in `cncrs`
cnmap_counties %>% ggplot() + geom_sf() + coord_sf(crs = cncrs)
```

### `cnmap_9dx` and `cnmap_islands`

Far-sea islands and south China sea boundary.

```{r}
library(sf)
sf_use_s2(F)

cnmap_provinces <- cnmap_counties %>% group_by(Code_Province) %>% 
  summarise(geometry = st_union(geometry))

ggplot() + 
  geom_sf(data = cnmap_provinces) +
  geom_sf(data = cnmap_9dx, linewidth = 1) +
  geom_sf(data = cnmap_islands) +
  coord_sf(crs = cncrs)
```



## functions

### `larger_bbox()` 

Get a broader bounding box of a given sf/sfc object. The result is more suitable for generating a fishnet raster.

```{r}
st_bbox(cnmap_counties) %>% 
  stars::st_as_stars(dx = 0.1, dy = 0.1)

larger_bbox(cnmap_counties, precise = 0.1) %>% 
  stars::st_as_stars(dx = 0.1, dy = 0.1)

larger_bbox(cnmap_counties, precise = 10) %>% 
  stars::st_as_stars(dx = 10, dy = 10)
```

### `simple_date()`
`simple_date()` acquires a abbreviation of the date.
```{r}
simple_date()
simple_date(as.Date("2023-09-09"))
simple_date("2025-12-28")

# useful when generating file names
str_glue("./this_is_the_filename_with_creating_date_{simple_date()}.R")
```

### `force_path_validate()`
`force_path_validate()` checks the given file path to see whether it contains any non-existing folder. If yes, this function automatically creates the folder(s) to ensure the path is available. Useful when generating a file name for saving.
```{r}
writeLines("abc", force_path_validate("~/THE/FILE/PATH/THAT/YOU/WANT/TO/TEST.abc"))
```

see results, run blow code:
```r
utils::browseURL("~/THE/FILE/PATH/THAT/YOU/WANT/TO/")
```

### `convert_amount()`
Convert and reform the values between some Chinese quantifiers

```{r}
convert_amount(66, "兆瓦", "万千瓦")

convert_amount(1.7, "米", "毫米")

convert_amount(9600000, "平方公里", "平方米")
```

### `convert_coord()`
Convert a set of geo-coding (long, lat) between some Chinese defined coordinate systems and WGS1984 coordinate system. Note that only works inside China domain.

```{r}
convert_coord(133, 47, from = "GCJ02", to = "WGS84")
```


### `Evantheme()`

A Yifan LIU-defined ggplot theme, already applied into my publications.

```{r}
ggplot() + 
  geom_sf(data = cnmap_provinces) +
  geom_sf(data = cnmap_9dx, linewidth = 1) +
  geom_sf(data = cnmap_islands) +
  coord_sf(crs = cncrs) +
  scale_x_continuous(name = "Longitude") +
  scale_y_continuous(name = "Latitude") +
  Evantheme()

```
